---
title: "Data 607 Project 3"
author: "Ajay Arora"
date: "October 4, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown
```{r}
install.packages("wordcloud") # word-cloud generator 
```
```{r}
library("wordcloud")
```

#Introduction

This task, in Data 607 Project 3, attempts to illuminate the necessary set of specific skills required to effectively work as a Data Scientist.  The task is to explore variety of publicly available data to perform analysis to determine which set of skills are ranked the highest.  To narrow the focus of this study, the analysis will be conducted on specific software tools and computing skills.  See Data and Variables of Measurement for additional information. 

#Team Members

Mario Pena    

Ajay Arora

#Initial Communication / Establishing Work Activity

We established communication over #Slack and spoke over the phone to introduce ourselves properly.  Furthermore, we divided the work effort in half.  The work effort consisted of Data Preparation, Data Cleaning, Data Analysis, and Conclusion.


#Ongoing Communication / Artifact Location

We both decided to communicate via email and/or #Slack.  In addition, we establihed a Project 3 group folder on GitHub.  

  https://github.com/AjayArora35/Data-607-Group-Project-3

  https://data607fall2019.slack.com/
  
#Data

The data was acquired at Kaggle.com.  (https://www.kaggle.com/discdiver/datasets) The specific software tools skills and computing skills were gathered from the following job posting sites, as indicated in the following image. The focus of the study is on specific software tools skills and computing skills described next. 

```{r}
sites <- c("LinkedIn", "Indeed", "Monster", "SimplyHired", "AngelList")
site_freq <- c(1, 1, 1, 1, 1)
set.seed(1234)
wordcloud(words = sites, freq = site_freq, min.freq = 1,
          max.words=200, random.order=FALSE, rot.per=0.35, 
          colors=brewer.pal(8, "Dark2"))
```

#Variables of Measurement
The following software tools skills are analyzed to determine their importance and/or ranking.

Python
SQL
R
Java 
Hadoop
Spark
Excel
Tableau
AWS
SAS
Scala
C++
Hive
Javascript
NoSQL
Azure
TensorFlow
C
PowerPoint
Matlab
Docker
Git
C# 
MySQL
Ruby
Microsoft Office
SPSS
MongoDB
Pig
Pandas
Hbase
Cassandra
Numpy
Perl
Power BI
Node
PostgreSQL
D3
Keras
PHP
Redis
Alteryx
Jupyter
Stata
Caffe
PyTorch

### The following computing skills are analyzed to determine their importance and/or ranking.
machine learning
analysis
statistics
computer science
communication
mathematics
visualization
AI composite
deep learning
NLP composite
software development
neural networks
data engineering
project management
software engineering


#Preparing Environment
```{r}
#Loading Libraries
library("knitr")
library("tidyverse")
library("tidyr")
library("dplyr")
library("stringr")
library("plotly")
library("htmlTable")
library("stringr")
library("ggplot2")
library("stats")
library(kableExtra)
library('scales')

```

#Data Preparation
##Read Software skills and Computing skills data from GitHub
```{r}
data <- read.csv(file="https://raw.githubusercontent.com/AjayArora35/Data-607-Group-Project-3/master/Data Science Software Skills.csv", header=TRUE, stringsAsFactors = FALSE)

data2C <- read.csv(file="https://raw.githubusercontent.com/AjayArora35/Data-607-Group-Project-3/master/Data Science Computing Skills.csv", header=TRUE, stringsAsFactors = FALSE)
```

###Sample data from Software Skills and Computing Skills
```{r}
head(data) %>% kable() %>%  kable_styling()

head(data2C) %>% kable() %>%  kable_styling()

```
#Data Cleaning 
##Remove commas, and fill in 0's for missing values
```{r}


data$LinkedIn <- as.numeric(gsub(",","",data$LinkedIn))
data$Indeed <- as.numeric(gsub(",","",data$Indeed))
data$Monster <- as.numeric(gsub(",","",data$Monster))
data$SimplyHired <- as.numeric(gsub(",","",data$SimplyHired))
data[is.na(data)] <- 0

data2C$LinkedIn <- as.numeric(gsub(",","", data2C$LinkedIn))
data2C$Indeed <- as.numeric(gsub(",","", data2C$Indeed))
data2C$SimplyHired <- as.numeric(gsub(",","", data2C$SimplyHired))
data2C$Monster <- as.numeric(gsub(",","", data2C$Monster))
data2C[is.na(data2C)] <- 0


head(data) %>% kable() %>%  kable_styling()

head(data2C) %>% kable() %>%  kable_styling()

```

#Analysis -- Software Skills
###LinkedIn Software Tool Favorability Ranking
```{r}
data2 <- data %>% 
  mutate(total = sum(data$LinkedIn),
         Favorability = percent(data$LinkedIn/total*100, accuracy = .01, scale=1))

data2 <- data2[order(-data2$LinkedIn),]

data2$Ranked <- 1:length(data2$LinkedIn)

         
select (data2, Keyword, LinkedIn, Favorability, Ranked)
```

###Indeed Software Tool Favorability Ranking
```{r}
data3 <- data %>% 
  mutate(total = sum(data$Indeed),
         Favorability = percent(data$Indeed/total*100, accuracy = .01, scale=1))

data3 <- data3[order(-data3$Indeed),]

data3$Ranked <- 1:length(data3$Indeed)


select (data3, Keyword, Indeed, Favorability, Ranked)
```

###Monster Software Tool Favorability Ranking
```{r}
data4 <- data %>% 
  mutate(total = sum(data$Monster),
         Favorability = percent(data$Monster/total*100, accuracy = .01, scale=1))

data4 <- data4[order(-data4$Monster),]

data4$Ranked <- 1:length(data4$Monster)

select (data4, Keyword, Monster, Favorability, Ranked)
```


###SimplyHired Software Tool Favorability Ranking
```{r}
data5 <- data %>% 
  mutate(total = sum(data$SimplyHired),
         Favorability = percent(data$SimplyHired/total*100, accuracy = .01, scale=1))

data5 <- data5[order(-data5$SimplyHired),]

data5$Ranked <- 1:length(data5$SimplyHired)


select (data5, Keyword, SimplyHired, Favorability, Ranked)
```

###AngelList Software Tool Favorability Ranking
```{r}
data6 <- data %>% 
  mutate(total = sum(data$AngelList),
         Favorability = percent(data$AngelList/total*100, accuracy = .01, scale=1))


data6 <- data6[order(-data6$AngelList),]

data6$Ranked <- 1:length(data6$AngelList)


select (data6, Keyword, AngelList, Favorability, Ranked)
```

###What is the most relevant software tool identified by LinkedIn?
```{r}
grid1 <- ggplot(data,
       aes(x=reorder(data$Keyword, data$LinkedIn),
           y=data$LinkedIn
           ))+
   geom_bar(stat = "identity", fill = "blue") + geom_text(aes(label=data$LinkedIn), vjust=0) +
  labs(title = "LinkedIn",
       x = "Software Tools", y = "Tool Relevance")+
  coord_flip()
grid1
```

###What is the most relevant software tool identified by Indeed?
```{r}
grid2 <- ggplot(data,
       aes(x=reorder(data$Keyword, data$Indeed),
           y=data$Indeed
           ))+
   geom_bar(stat = "identity", fill = "dark green") + geom_text(aes(label=data$Indeed), vjust=0) +
  labs(title = "Indeed",
       x = "Software Tools", y = "Tool Relevance")+
  coord_flip()

```

###What is the most relevant software tool identified by Monster?
```{r}
grid3 <- ggplot(data,
       aes(x=reorder(data$Keyword, data$Monster),
           y=data$Monster
           ))+
   geom_bar(stat = "identity", fill = "purple") + geom_text(aes(label=data$Monster), vjust=0) +
  labs(title = "Monster",
       x = "Software Tools", y = "Tool Relevance")+
  coord_flip()

```

###What is the most relevant software tool identified by SimplyHired?
```{r}
grid4 <- ggplot(data,
       aes(x=reorder(data$Keyword, data$SimplyHired),
           y=data$SimplyHired
           ))+
   geom_bar(stat = "identity", fill = "coral") + geom_text(aes(label=data$SimplyHired), vjust=0) +
  labs(title = "SimplyHired",
       x = "Software Tools", y = "Tool Relevance")+
  coord_flip()

```

###What is the most relevant software tool identified by AngelList?
```{r}
grid5 <- ggplot(data,
       aes(x=reorder(data$Keyword, data$AngelList),
           y=data$AngelList
           ))+
   geom_bar(stat = "identity", fill = "pink") + geom_text(aes(label=data$AngelList), vjust=0) +
  labs(title = "AngelList",
       x = "Software Tools", y = "Tool Relevance")+
  coord_flip()

```


```{r}
require(gridExtra)
grid.arrange(grid1, grid2, grid3, grid4, grid5, ncol=2)
```




#Analysis -- Computing Skills

###LinkedIn Computing Skill Favorability Ranking
```{r}

data22 <- data2C %>% 
  mutate(total = sum(data2C$LinkedIn),
         Favorability = percent(data2C$LinkedIn/total*100, accuracy = .01, scale=1))


data22 <- data22[order(-data22$LinkedIn),]

data22$Ranked <- 1:length(data22$LinkedIn)


select (data22, Keyword, LinkedIn, Favorability, Ranked)

```

###Indeed Computing Skill Favorability Ranking
```{r}
data23 <- data2C %>% 
  mutate(total = sum(data2C$Indeed),
         Favorability = percent(data2C$Indeed/total*100, accuracy = .01, scale=1))

data23 <- data23[order(-data23$Indeed),]

data23$Ranked <- 1:length(data23$Indeed)

select (data23, Keyword, Indeed, Favorability, Ranked)
```

###Monster Computing Skill Favorability Ranking
```{r}
data24 <- data2C %>% 
  mutate(total = sum(data2C$Monster),
         Favorability = percent(data2C$Monster/total*100, accuracy = .01, scale=1))

data24 <- data24[order(-data24$Monster),]

data24$Ranked <- 1:length(data24$Monster)

select (data24, Keyword, Monster, Favorability, Ranked)
```


###SimplyHired Computing Skill Favorability Ranking
```{r}
data25 <- data2C %>% 
  mutate(total = sum(data2C$SimplyHired),
         Favorability = percent(data2C$SimplyHired/total*100, accuracy = .01, scale=1))

data25 <- data25[order(-data25$SimplyHired),]

data25$Ranked <- 1:length(data25$SimplyHired)

select (data25, Keyword, SimplyHired, Favorability, Ranked)
```


###What is the most relevant Computing Skill identified by LinkedIn?
```{r}
grid21 <- ggplot(data2C,
       aes(x=reorder(data2C$Keyword, data2C$LinkedIn),
           y=data2C$LinkedIn
           ))+
   geom_bar(stat = "identity", fill = "blue") + geom_text(aes(label=data2C$LinkedIn), vjust=0) +
  labs(title = "LinkedIn",
       x = "Computing Skills", y = "Skill Relevance")+
  coord_flip()
grid21
```

###What is the most relevant Computing Skill identified by Indeed?
```{r}
grid22 <- ggplot(data2C,
       aes(x=reorder(data2C$Keyword, data2C$Indeed),
           y=data2C$Indeed
           ))+
   geom_bar(stat = "identity", fill = "dark green") + geom_text(aes(label=data2C$Indeed), vjust=0) +
  labs(title = "Indeed",
       x = "Computing Skills", y = "Skill Relevance")+
  coord_flip()
grid22
```

###What is the most relevant Computing Skill identified by Monster?
```{r}
grid23 <- ggplot(data2C,
       aes(x=reorder(data2C$Keyword, data2C$Monster),
           y=data2C$Monster
           ))+
   geom_bar(stat = "identity", fill = "purple") + geom_text(aes(label=data2C$Monster), vjust=0) +
  labs(title = "Monster",
       x = "Computing Skills", y = "Skill Relevance")+
  coord_flip()
grid23
```


###What is the most relevant Computing Skill identified by SimplyHired?
```{r}
grid24 <- ggplot(data2C,
       aes(x=reorder(data2C$Keyword, data2C$SimplyHired),
           y=data2C$SimplyHired
           ))+
   geom_bar(stat = "identity", fill = "pink") + geom_text(aes(label=data2C$SimplyHired), vjust=0) +
  labs(title = "SimplyHired",
       x = "Computing Skills", y = "Skill Relevance")+
  coord_flip()
grid24
```




```{r}
require(gridExtra)
grid.arrange(grid21, grid22, grid23, grid24,  ncol=2)
```

#Conclusions

Although this study is not based on a scientific inquiry with control mechanisms in place, however, the anecdotal evidence cannot be overlooked regarding the current trending of data science software and computing skills.  Before we discuss any of the findings, it is worth bearing in mind, the unequal respondants distribution among the different job positing sites.  For example, LinkedIn enjoys much larger audience than AngelList.  These unequal distributions are worth keeping in minds as we dicuss some final numbers.  Furthermore, it is worth keeping in mind, whether mechanisms were in place to prevent a user respondent from submitting more than once per question.  

LinkedIn, Indeed, SimplyHired, and AngelList, the computing practitioners respondants, chose Python as their most relevant Data Science software tools skills.  However, there was one exception with Monster.  The participants at Monster chose SQL as the top software tool skill.  