---
title: "Data 607 Project 3"
author: "Ajay Arora"
date: "October 4, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

#Introduction

This task, in Data 607 Project 3, attempts to illumniate the necessary set of specific skills required to effectively work as a Data Scientist.  The task is to explore variety of publicly available data to perform analysis to determine which set of skills are ranked the highest.  To narrow the focus of this study, the analysis will be conducted on specific software tools and "soft" skills.  See Data and Variables of Measurement for additional information. 

#Team Members

Mario Pena    

Ajay Arora

#Initial Communication / Establishing Work Activity

We established communication over #Slack and spoke over the phone to introduce ourselves properly.  Furthermore, we divided the work effort in half.  The work effort consisted of Data Preparation, Data Cleaning, Data Analysis, and Conclusions.


#Ongoing Communication / Artifact Location

We both decided to communicate via email and/or #Slack.  In addition, we establihed a Project 3 group folder on GitHub.  

  https://github.com/AjayArora35/Data-607-Group-Project-3

  https://data607fall2019.slack.com/
  
#Data

The data was acquired at Kaggle.com.  (https://docs.google.com/spreadsheets/d/1lac1H2IgCDCs9LLTQL6yb6MUPN1u4C5fJv_6YjipIaM/edit#gid=0) The specific software tools skills were gathered from LinkedIn, Indeed, Monster, SimplyHired, and AngelList. The focus of the study is on specific software tools skills described next. 

#Variables of Measurement
The following software tools skills are analyzed to determine their importance and/or ranking.

Python
SQL
R
Java 
Hadoop
Spark
Excel
Tableau
AWS
SAS
Scala
C++
Hive
Javascript
NoSQL
Azure
TensorFlow
C
PowerPoint
Matlab
Docker
Git
C# 
MySQL
Ruby
Microsoft Office
SPSS
MongoDB
Pig
Pandas
Hbase
Cassandra
Numpy
Perl
Power BI
Node
PostgreSQL
D3
Keras
PHP
Redis
Alteryx
Jupyter
Stata
Caffe
PyTorch




#Preparing Environment
```{r}
#Loading Libraries
library("knitr")
library("tidyverse")
library("tidyr")
library("dplyr")
library("stringr")
library("plotly")
library("htmlTable")
library("stringr")
library("ggplot2")
library("stats")
library(kableExtra)
library('scales')

```

#Data Preparation
##Read data from GitHub
```{r}
data <- read.csv(file="https://raw.githubusercontent.com/AjayArora35/Data-607-Group-Project-3/master/Data Science Software Skills.csv", header=TRUE, stringsAsFactors = FALSE)

head(data) %>% kable() %>%  kable_styling()

```
#Data Cleaning 
##Remove commas, and fill in 0's for missing values
```{r}


data$LinkedIn <- as.numeric(gsub(",","",data$LinkedIn))
data$Indeed <- as.numeric(gsub(",","",data$Indeed))
data$Monster <- as.numeric(gsub(",","",data$Monster))
data$SimplyHired <- as.numeric(gsub(",","",data$SimplyHired))
data[is.na(data)] <- 0

head(data) %>% kable() %>%  kable_styling()
```

#Analysis
###LinkedIn Software Tool Favorability Ranking
```{r}
data2 <- data %>% 
  mutate(total = sum(data$LinkedIn),
         Favorability = percent(data$LinkedIn/total*100, accuracy = .01, scale=1),
         Ranked = rank((1:length(data$LinkedIn)))) 

select (data2, Keyword, LinkedIn, Favorability, Ranked)
```

###Indeed Software Tool Favorability Ranking
```{r}
data3 <- data %>% 
  mutate(total = sum(data$Indeed),
         Favorability = percent(data$Indeed/total*100, accuracy = .01, scale=1),
         Ranked = rank((1:length(data$Indeed)))) 

select (data3, Keyword, Indeed, Favorability, Ranked)
```

###Monster Software Tool Favorability Ranking
```{r}
data4 <- data %>% 
  mutate(total = sum(data$Monster),
         Favorability = percent(data$Monster/total*100, accuracy = .01, scale=1),
         Ranked = rank((1:length(data$Monster)))) 

select (data4, Keyword, Monster, Favorability, Ranked)
```


###SimplyHired Software Tool Favorability Ranking
```{r}
data5 <- data %>% 
  mutate(total = sum(data$SimplyHired),
         Favorability = percent(data$SimplyHired/total*100, accuracy = .01, scale=1),
         Ranked = rank((1:length(data$SimplyHired)))) 

select (data5, Keyword, SimplyHired, Favorability, Ranked)
```

###AngelList Software Tool Favorability Ranking
```{r}
data6 <- data %>% 
  mutate(total = sum(data$AngelList),
         Favorability = percent(data$AngelList/total*100, accuracy = .01, scale=1),
         Ranked = rank((1:length(data$AngelList)))) 

select (data6, Keyword, AngelList, Favorability, Ranked)
```

###What is the most relevant software tool identified by LinkedIn?
```{r}
grid1 <- ggplot(data,
       aes(x=reorder(data$Keyword, data$LinkedIn),
           y=data$LinkedIn
           ))+
   geom_bar(stat = "identity", fill = "blue") + geom_text(aes(label=data$LinkedIn), vjust=0) +
  labs(title = "LinkedIn",
       x = "Software Tools", y = "Tool Relevance")+
  coord_flip()
grid1
```

###What is the most relevant software tool identified by Indeed?
```{r}
grid2 <- ggplot(data,
       aes(x=reorder(data$Keyword, data$Indeed),
           y=data$Indeed
           ))+
   geom_bar(stat = "identity", fill = "dark green") + geom_text(aes(label=data$Indeed), vjust=0) +
  labs(title = "Indeed",
       x = "Software Tools", y = "Tool Relevance")+
  coord_flip()

```

###What is the most relevant software tool identified by Monster?
```{r}
grid3 <- ggplot(data,
       aes(x=reorder(data$Keyword, data$Monster),
           y=data$Monster
           ))+
   geom_bar(stat = "identity", fill = "purple") + geom_text(aes(label=data$Monster), vjust=0) +
  labs(title = "Monster",
       x = "Software Tools", y = "Tool Relevance")+
  coord_flip()

```

###What is the most relevant software tool identified by SimplyHired?
```{r}
grid4 <- ggplot(data,
       aes(x=reorder(data$Keyword, data$SimplyHired),
           y=data$SimplyHired
           ))+
   geom_bar(stat = "identity", fill = "coral") + geom_text(aes(label=data$SimplyHired), vjust=0) +
  labs(title = "SimplyHired",
       x = "Software Tools", y = "Tool Relevance")+
  coord_flip()

```

###What is the most relevant software tool identified by AngelList?
```{r}
grid5 <- ggplot(data,
       aes(x=reorder(data$Keyword, data$AngelList),
           y=data$AngelList
           ))+
   geom_bar(stat = "identity", fill = "pink") + geom_text(aes(label=data$AngelList), vjust=0) +
  labs(title = "AngelList",
       x = "Software Tools", y = "Tool Relevance")+
  coord_flip()

```


```{r}
require(gridExtra)
grid.arrange(grid1, grid2, grid3, grid4, grid5, ncol=2)
```

